---
title: "Erdenebileg_S4662976"
author: "Erdenebileg"
date: "23/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Part 1: formatting RMarkdown document
*Erdenebileg*


## ID-S4662976 



# Assignment 2
)

### Part 2 Data Wrangling and visualization 

```{r}
install.packages("tidyverse")
install.packages("randomForest")
install.packages("widyr")
install.packages("forcats")
install.packages("skimr")
install.packages("modeldata")
library(tidyverse)
library(skimr)
library(knitr)
library(modeldata)
library(forcats)
library(widyr)


Data_thanksgiving_meal <-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")
```

###p Part 2 
### Q 1
```{r}
# Display the first 10 rows of the dataset using `kable()` function. 
kable(head(Data_thanksgiving_meal,10))

```



### Q 2
```{r}
 #Using `skim()` display the summary of variables.
summary(Data_thanksgiving_meal)
skim(Data_thanksgiving_meal)
```
### Think about the task to predict a family income based on their menu: what variables may be useful? Are all of them correct type? 
How much expensive meal they consume show us their family income. Based on the data set, Main_dish, side8, pie13 and dessert1 are  useful data.
```
```

### Think about the task to predict a community type or US_region based on their menu: what variables may be useful? Are all of them correct type?

### Q 3
```{r}
#Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`
family_income <- Data_thanksgiving_meal %>%
   mutate(family_income = fct_reorder(family_income,      parse_number(family_income)))

skim(family_income)
```

### Q 4
```{r}
#What is the number of people who celebrate?
nrow(subset(Data_thanksgiving_meal, celebrate=='Yes'))
```

### Q 5
```{r}
#  What are categories and insights for each main dish served and the method it is prepared?
knitr::kable(Data_thanksgiving_meal %>% 
               group_by(main_dish) %>% 
               count(main_prep) %>% 
               arrange(desc(n)) %>% 
               head(n=10))
```

### Q 6
```{r}
# Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes.
Write 2-3 sentences with your explanation of each insight.

Data_thanksgiving_meal %>% 
  ggplot(aes(x = main_dish, fill = main_dish)) +     geom_bar() + 
  labs(x = "Main Dish", y = "Count", title = "Display main dish and Method it is prepared", subtitle = "Main Dish", caption = "Display main dish and Method it is prepared",  fill = "Viz1")+
  theme_classic()
```



# Viz 2
```{r}

 Data_thanksgiving_meal %>%
   ggplot(aes(main_dish, main_prep)) +
   geom_count(size=2, color="red") +
   labs(X = "Main_dish", 
        y = " Count", title = "Viz2") +
   theme_light()
```

   
   #viz3 


### Q 7
```{r}
#How many use cranberry sauce
nrow(subset(Data_thanksgiving_meal, cranberry=='Canned' | cranberry=='Homemade'))
```
# How many use gravy

```{r}

nrow(subset(Data_thanksgiving_meal, gravy=='Yes'))
```

### Q 8-9

```{r}
#  What is the distribution of those who celebrate across income ranges. Create a data viz.
Write 2-3 sentences with your explanation of each insight.
Data_thanksgiving_meal %>% ggplot() +  
  aes(x = celebrate, fill =family_income) +  
  geom_bar() + 
  labs(x = "celebrate", y = "Count", title = "Distribution of those who celebrate across income ranges", subtitle = "Celebrate", caption = "Distribution of those who celebrate across income ranges",  fill = "Viz1")+
  theme_grey()

```
###Families income  between 0$- more than 200000$  families  celebrate thanksgiving. Among them, most percentages of  familes have 25000$-50000$ income. 

### Q 10
```{r}
New_data_set <- Data_thanksgiving_meal %>%
select(id, starts_with("side"),
         starts_with("pie"),
         starts_with("dessert")) %>%
  select(-side8, -pie13, -dessert1) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))

```
### First, Select column and colomn-id with pie, side, dessert.Second, Choose Side8,pie13 and dessrt1.Third, Gather type, value and id.Fourt, Delete None and other(please specify).

### Q 11

### Q 12
```{r}
#Intall package `widyr` and use `pairwise_cor()` function https://www.rdocumentation.org/packages/widyr/versions/0.1.3/topics/pairwise_cor
#Write 2-3 sentences with your explanation of what it does.

New_data_set %>%
  pairwise_cor(value, id, sort = TRUE)
```

### Q 13
#Use `lm()` or randomForest() function to build a model that predict a family income based on data in the dataset
```{r}

install.packages("linearModel")
library(linearModel)
skim(family_income)
data(Data_thanksgiving_meal)
## Regression Model 1

lm <- lm(family_income ~ dessert1, Data_thanksgiving_meal, na.action = na.omit)

summary(lm)
```
# Regression Model 2
```{r}
lm1 <- lm(family_income ~ dessert1 + pie1, Data_thanksgiving_meal, na.action = na.omit)

summary(lm1)
```
```{r}
# Regression Model 2
lm2 <- lm(family_income ~ dessert1+pie1+ side1, Data_thanksgiving_meal, na.action = na.omit)

summary(lm2)
```
#### Resources:

RMarkdown tutorial https://rmarkdown.rstudio.com/lesson-1.html

ggplot2: Elegant Graphics for Data Analysis https://ggplot2-book.org/
